\documentclass[12pt, a4paper]{article}
%\usepackage{geometry}
\usepackage[inner=1.0cm,outer=1.0cm,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{empty}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw, tabularx}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.7,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{\textsc{EDI 3400: Programming and Data Management} }}
\chead{ \fancyplain{}{} }
\rhead{ \fancyplain{}{\textsc{Course description} }}
%\rfoot{\fancyplain{}{page \thepage\ of \pageref{LastPage}}}
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}

%%%%%%%%%%%% LISTING %%%
\usepackage{listings}
\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{verbatim} % used to display code
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm}
\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.93}
\lstset{
%language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=t,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
    {\LARGE \textsc{Programming and Data Management}}
\end{center}
\begin{center}
    Semester: Fall 2022\\
    %Program: Bachelor of Digital Business\\
    Course code: EDI 3400 \\
    BI Norwegian Business School\\
    {\small This version: \today}
\end{center}
%\date{September 26, 2014}

\begin{center}
    \rule{\textwidth}{0.4pt}
    \begin{minipage}[t]{\textwidth}
        \medskip
        \begin{tabularx}{\linewidth}{XXXX}
            \textbf{Instructor:}  & Vegard H. Larsen                                                                    & \textbf{Contact:}      & \href{mailto:vegard.h.larsen@bi.no}{vegard.h.larsen@bi.no} \medskip \\
            \textbf{Office:}      & B3Y-097                                                                             & \textbf{Office Hours:} & Wednesdays 10 -- 12  \medskip                                       \\
            \textbf{Course Pages} & \href{https://bi.itslearning.com/main.aspx?TextURL=CourseCards}{bi.itslearning.com} & \textbf{TA:}           & Lorenzo Gaviano \medskip                                            \\
        \end{tabularx}\medskip
    \end{minipage}
    \rule{\textwidth}{0.4pt}
\end{center}
\vspace{.2cm}
\setlength{\unitlength}{1in}
\renewcommand{\arraystretch}{2}

\noindent
This course introduces Python and SQL, two of the most popular and indispensable programming languages for data analysts.
In addition, the course covers the basics of data management with focus on relational databases.

\vskip.25in
\noindent\textbf{\large Compulsory Readings}
\begin{enumerate}
    \item Python for everybody: exploring data using Python 3 by \it{Charles R. Severance}
          (\href{https://www.py4e.com/book.php}{Link})
    \item Introduction to Python for Econometrics, Statistics and Data Analysis by \it{Kevin Sheppard}
          (\href{https://www.kevinsheppard.com/files/teaching/python/notes/python_introduction_2021.pdf}{Link})
    \item SQL queries for mere mortals: a hands-on guide to data manipulation in SQL by \it{John L. Viescas}
\end{enumerate}

\vskip.25in
\noindent\textbf{\large Software} \\
In this course we will mainly be using Python.
We will install Python through the Anaconda distribution.
You can run into some problems if you don't have the correct version of the software installed.
Try to install the latest version you find. Python 2 will not be supported.
\begin{enumerate}
    \item \href{https://www.anaconda.com/}{Anaconda}
    \item \href{https://sqlitebrowser.org/}{DB Browser for SQLite}
          %\item MySQL community server, \url{https://dev.mysql.com/downloads/}
          %\item MySQL Workbench, \url{https://dev.mysql.com/downloads/}
\end{enumerate}

\vskip.15in
\noindent\textbf{\large Supplementary Material} \\%\footnotemark
Here are some interesting resources that will be useful during the course.
This is not mandatory readings.
\begin{itemize}
    \item \href{https://docs.python.org/3/tutorial/}{Python tutorial}
    \item \href{https://jupyter-notebook.readthedocs.io/}{Jupyter Notebook documentation}
    \item \href{https://numpy.org/doc/}{NumPy documentation}
    \item \href{https://pandas.pydata.org/docs/}{Pandas documentation}
    \item \href{https://matplotlib.org/stable/users/index}{Matplotlib documentation}
    \item \href{https://docs.python.org/3/library/sqlite3.html}{SQLite Python API documentation}
\end{itemize}

\newpage
\noindent\textbf{\large Lecture Plan}\\
Lectures are always from 10:00 -- 11:45.
\begin{enumerate}
    \item[] \underline{Lecture 1:} [Friday, Sep. 2., D3-080] {\bf Introduction to Python and the Jupyter Notebook}
        \begin{itemize}
            \item Ch.1 of {\it Severance} and Ch.1 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 2:} [Tuesday, Sep. 6., B2-060] {\bf Variables, expressions, and statements}
        \begin{itemize}
            \item Ch.2 and Ch.3 of {\it Severance} and Ch.2, Ch.4 and Ch.10 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 3:} [Wednesday, Sep. 7., C1-050] {\bf Built in functions, lists, strings, dict's and sets}
        \begin{itemize}
            \item Ch.4, Ch.6, Ch.8, Ch.9, Ch.10 of {\it Severance} and Ch.23 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 4:} [Tuesday, Sep. 13., B2-060] {\bf Loops and flow control, input and output}
        \begin{itemize}
            \item Ch.3, Ch.5, Ch.7, Ch.11 of {\it Severance} and Ch. 12 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 5:} [Wednesday, Sep. 14., C1-050] {\bf The Standard Library, Functions and Classes}
        \begin{itemize}
            \item Ch.4, Ch.11, Ch.14 of {\it Severance} and Ch.29 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 6:} [Tuesday, Sep. 20., B2-060] {\bf 3rd party libraries (linear algebra): Numpy}
        \begin{itemize}
            \item Ch.3, Ch.5, Ch.6, Ch.7, Ch.11 and Ch.19 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 7:} [Wednesday Sep. 21., C1-050] {\bf 3rd party libraries (data frames): Pandas}
        \begin{itemize}
            \item Ch.8 and Ch.16 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 8:} [Tuesday, Sep. 27. B2-060] {\bf 3rd party libraries (graphics): Matplotlib and Seaborn}
        \begin{itemize}
            \item Ch.15 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 9:} [Tuesday, Oct 5., D3-191] {\bf Working with data, dates and time, and web scraping}
        \begin{itemize}
            \item Ch.14, Ch.15 and Ch.16 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 10:} [Tuesday, Oct. 11., B2-060] {\bf Analyzing data, probability and statistics}
        \begin{itemize}
            \item Ch.19 and Ch.20 of {\it Sheppard}
        \end{itemize}
    \item[] \underline{Lecture 11:} [Tuesday, Oct. 18., B2-060] {\bf Introduction to relational databases}
        \begin{itemize}
            \item Ch.15 of {\it Severance} and Ch.1, Ch.2, Ch.3 of {\it Viescas}
        \end{itemize}
    \item[] \underline{Lecture 12:} [Tuesday, Oct 25., B2-060] {\bf SQL Basics}
        \begin{itemize}
            \item Ch.4, Ch.5 and Ch.6 of {\it Viescas}
        \end{itemize}
    \item[] \underline{Lecture 13:} [Tuesday, Nov 1., B2-060] {\bf Python and SQL}
        \begin{itemize}
            \item Ch.15 of {\it Severance}
        \end{itemize}
    \item[] \underline{Lecture 14:} [Tuesday, Nov 8., B2-060] {\bf Summing up and Q\&A}
\end{enumerate}

\newpage
\noindent\textbf{\large Asynchronous learning: Homework/Projects} \\
You will have four homeworks/projects that will be given as Jupyter Notbooks.
They will not be graded but you are expected to finish all of them.
They can be solved individually or in groups of 2-3 students.
Solutions will be provided some weeks after you get the homeworks.
Everything will be made available at itslearning.
\begin{enumerate}
    \item Programming with basic Python
    \item 3rd party libraries
    \item Working with data in Python
    \item Databases with SQL and Python
\end{enumerate}

\vskip.25in
\noindent\textbf{\large Exercise Sessions} \\
Exercise sessions are always on Wednesdays from 12:00 -- 13:45.
\begin{enumerate}
    \item[] \underline{Exercise 1:} [Sep. 7., D3-080] {\bf Installing the Jupyter Notebook}
    \item[] \underline{Exercise 2:} [Sep. 14., D3-080] {\bf Installing the Jupyter Notebook}
    \item[] \underline{Exercise 3:} [Sep. 21., D3-037] {\bf Programming with basic Python}
    \item[] \underline{Exercise 4:} [Sep. 28., D3-037] {\bf Homework 1}
    \item[] \underline{Exercise 5:} [Oct. 5., D3-037]  {\bf 3rd party libraries}
    \item[] \underline{Exercise 6:} [Oct, 12., D3-037] {\bf Homework 2}
    \item[] \underline{Exercise 7:} [Oct. 19., D3-037] {\bf Working with data in Python}
    \item[] \underline{Exercise 8:} [Oct. 26., D3-037] {\bf Homework 3}
    \item[] \underline{Exercise 9:} [Nov. 2., B3-037] {\bf Databases with SQL and Python}
    \item[] \underline{Exercise 10:} [Nov. 9., D3-037] {\bf Homework 4}
\end{enumerate}

\vskip.25in
\noindent\textbf{\large Exam}
\begin{itemize}
    \item Exam format: 30 hour take-home exam
    \item Start: 19.12.2022 at 09:00
    \item Submission deadline: 20.12.2022 at 15:00
\end{itemize}

\end{document}